Reanalysis Step 3: Propensity Score Analysis with Twang

### 2025-08-19 reanalysis-3-propensity_scores.qmd
debug ps

# Set parameters based on mode
if (analysis_mode == "test") {
  max_imputations_to_process <- 2  # Process only 2 imputations in test mode
  max_imputations_for_diagnostics <- 2  # Show diagnostics for 2 imputations in test
  n_trees <- 1000  # Fewer trees for testing
} else {
  max_imputations_to_process <- NULL  # Process all available imputations
  max_imputations_for_diagnostics <- 5  # Show diagnostics for up to 5 imputations in final
  n_trees <- 3000  # More trees for final analysis
}

@@

  cat("#### Convergence (Iteration Plot)\n\n")
  # Plot 1: Shows how balance metrics change across iterations
  plot(twang_model, plots = 1)
  cat("\n\n")

  cat("#### Weight Distribution (Boxplot)\n\n")
  # Plot 2: Shows distribution of weights
  plot(twang_model, plots = 2)
  cat("\n\n")

  cat("#### Covariate Balance (Standardized Mean Differences)\n\n")
  # Plot 3: Shows balance for each covariate
  plot(twang_model, plots = 3)
  cat("\n\n")

  cat("#### Alternative Balance Plot (Love Plot)\n\n")
  # Use cobalt for better visualization
  library(cobalt)
  love_plot <- love.plot(
    bal.tab(ps_formula, 
            data = data_with_weights,
            weights = "weights",
            estimand = "ATT",
            s.d.denom = "treated"),
    thresholds = c(m = 0.1),
    title = paste("Covariate Balance - Imputation", i)
  )
  print(love_plot)
  cat("\n\n")

  cat("#### Weight Proportions\n\n")
  # Plot 6: Histogram of weight proportions
  plot(twang_model, plots = 6)
  cat("\n\n")

>>>>

# Set parameters based on mode
if (analysis_mode == "test") {
  max_imputations_to_process <- 1  # Process only 2 imputations in test mode
  max_imputations_for_diagnostics <- 1  # Show diagnostics for 2 imputations in test
  n_trees <- 1000  # Fewer trees for testing
} else {
  max_imputations_to_process <- NULL  # Process all available imputations
  max_imputations_for_diagnostics <- 5  # Show diagnostics for up to 5 imputations in final
  n_trees <- 3000  # More trees for final analysis
}

@@

  cat("#### Convergence (Iteration Plot)\n\n")
  # Plot 1: Shows how balance metrics change across iterations
  print(plot(twang_model, plots = 1))
  cat("\n\n")

  cat("#### Weight Distribution (Boxplot)\n\n")
  # Plot 2: Shows distribution of weights
  print(plot(twang_model, plots = 2))
  cat("\n\n")

  cat("#### Covariate Balance (Standardized Mean Differences)\n\n")
  # Plot 3: Shows balance for each covariate
  print(plot(twang_model, plots = 3))
  cat("\n\n")

  cat("#### Alternative Balance Plot (Love Plot)\n\n")
  # Use cobalt for better visualization
  love_plot <- love.plot(
    bal.tab(ps_formula, 
            data = data_with_weights,
            weights = "weights",
            estimand = "ATT",
            s.d.denom = "treated"),
    thresholds = c(m = 0.1),
    title = paste("Covariate Balance - Imputation", i)
  )
  print(love_plot)
  cat("\n\n")

  cat("#### Weight Proportions\n\n")
  # Plot 6: Histogram of weight proportions
  print(plot(twang_model, plots = 6))
  cat("\n\n")
